\documentclass{letter}

\usepackage[margin=1in]{geometry}

\renewcommand{\familydefault}{\sfdefault}

\makeatletter
\def\ps@plain{%
\let\@oddfoot\@empty
\def\@oddhead{\fromname{}
\hfil \fromaddress{} \fromlocation{}
\hfil \telephonenum{}}%
\let\@evenfoot\@empty
\let\@evenhead\@oddhead}
\makeatother
\pagestyle{plain}

\renewcommand*{\opening}[1]{\vspace{2\parskip}%
#1 \toname,\hfill\today\par\nobreak
}
\renewcommand*{\closing}[1]{\par\nobreak\vspace{\parskip}%
\vspace{2\parskip}%
#1\\[6\medskipamount]%
\fromsig
}

\name{Pedro Rodrigues}
\signature{Pedro Rodrigues}
\address{Rua Lopes Mendonça nº12 6ºdto}
\location{Almada, Portugal}
\telephone{prodrigues1990@gmail.com}

\begin{document}
\begin{letter}{}

\textbf{AVL Emission Test Systems GmbH}\\
Graf-Landsberg-Strasse 1C\\
41460 Neuss\\
Germany\\

\textbf{Application for Information Technology Technician}

\opening{Dear}

I was made aware of your requirements for a technician skilled in computer science by my friend,
and your employee, Rafael Abreu Marques. Delighted to known such requirements, having a valuable
set of skills in the computer science field, and actively looking to move abroad, my name is Pedro
Rodrigues and with determination and confidence in delivering, I would like to spontaneously offer
my expertise to fulfill such requirements.

I've finished my school years in a proffessional course in management and programming of
information systems, where I've develop crucial skills and concepts in, computer languages mainly
focused in C\#.NET, database systems such as SQL, and computer networks principles and application
in Microsoft's solutions. Which was just the culmination of beeing fascinated with computers since
very early age.

During the final stages of the course, I've had been gathering know how in the various entreprise
used solutions, helping in management of a small datacenter, client VPN networks, and beeing part
from the beginning to product release of the largest Portuguese feed bank website. At Variograma,
I've also learned valuable team work knowledge and tools such software version control, and linux
operating systems, during a 6 month internship program.

By the end of the course I was confident in my capabilities, I was looking for an opportunity, and
discovered the vast world of open source software during the free time, where I started to
contribute. Culminating with the release of an extremely popular computer game addon written in C\#
as open source.

Still looking to improvement my qualities, I've enrolled in a technical course at PHC Portugal, a
software house and key player in Entreprise Resource Planning (ERP) software for the portuguese
market, focused on configuration of their ERP software, and heavily targetting extensibility with
custom designed procedures within. A key skillset to narrow my focus.

Applying all learned before, and with increased responsibility, I joined a team of 5 managers

Determined to make a difference, given the responsibility to reform their IT department and
accomodate PHC's ERP software into their existing processes, Casacon, an established construction
material reseller in Angola, allowed me the opportunity to move to Africa. Working and living with
a dedicated team for more than 2 years, I was able to fully apply and gain profound knowledge in
entreprise networks. Applying the concepts learned before, at a larger scale, and
with even greater responsibility. I've learned  with actual hardware providers for network and datacenter
enviroments such as DELL, Cisco, Juniper, and HP, as well as key software providers such as VMWare
and the, at time emerging, virtualization technologies.

In little over two years with Casacon, we've accomplished more than proposed and I was looking for
new opportunies. The workforce required for a reform in the IT department was no longer justified,
in a stable department with little day to day activities and it was decided to relief two
technicians working under my supervision, and pass my responsibilities to a subcontracter as my
proposal.

\closing{Your sincerely.}
\end{letter}
\end{document}
