%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Pedro}{Rodrigues}{ % Your name
\href{mailto:prodrigues1990@gmail.com}{prodrigues1990@gmail.com} \\ % Your website, LinkedIn profile or other web address
+351 969 042 335 | +244 917 774 823% Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth}

\section{Personal} 

Nacionality \textbf{Portuguese}\\
Age \textbf{24 Years}\\
Gender \textbf{Male}\\

\descript{Address}
Cond. Vila Recife, Apt. 1\\
Talatona, Muníncipio de Belas\\
Luanda, AO\\
\sectionspace{}
Rua Lopes Mendonça, nº12 6ºdto\\
2800-696 Almada\\
Setúbal, PT\\

\sectionspace

\section{Education}
\subsection{EPED}
\descript{Management and Programing of Information Technology Systems}
\location{2008 to 2010 | Almada, PT}
Microsoft network management\\
.NET Programming

\sectionspace

\section{Certifications}
\subsection{PHC Portugal}
\descript{Certified Technician PHC Advanced}
\location{2012 | Lisboa, PT}

\sectionspace

\section{Languages}
\descript{Mother:}
\location{Portuguese}
\descript{Foreign:}
\location{English}
Advanced knowledge with some publications. Some speech difficulty due to poor practice.

\section{Links}
\href{https://github.com/pedro2555}{GitHub://\textbf{pedro2555}}\\
\href{https://bitbucket.org/pedro2555}{BitBucket://\textbf{pedro2555}}\\
\href{https://www.youtube.com/channel/UCxvDHtW_fPVIPHXOBzxt6Fg}{YouTube://\textbf{Pedro Rodrigues}}\\
\href{https://plus.google.com/105867523802923906663/posts}{Google+://\textbf{Pedro Rodrigues}}\\

\end{minipage}
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth}

\section{Professional Experience}

\runsubsection{Casacon}
\descript{| IT Manager}

\location{August 2013 - Present | Luanda, AO}
\vspace{\topsep}
\begin{tightitemize}
	\item Responsible for the IT sector;
	\item Management software migration coordinator;
	\item Responsible for planning and execution of datacenter virtualization:
	\item Responsible for implementation of norms and regulation on IT resource usage;
	\item Responsible for implementation of company documentation flows and procedures.
\end{tightitemize}

\sectionspace

\runsubsection{Optimus}
\descript{| Comercial Consultant}

\location{February 2012 - April 2012 | Lisboa, PT}
\begin{tightitemize}
	\item Selling of Optimus products.
\end{tightitemize}

\sectionspace

\runsubsection{CEC}
\descript{| Comercial Consultant}

\location{April 2011 - January 2012 | Lisboa, PT}
\begin{tightitemize}
	\item Selling of Optimus products.
\end{tightitemize}

\sectionspace

\runsubsection{Freelancer}
\descript{| WEB Development}

\location{August 2010 - April 2011 | Almada, PT}
\begin{tightitemize}
	\item Tailor made software development;
	\item Development of \textit{web} bussiness solutions;
	\item Development of \href{http://esquicodeideias.com}{Esquiço de Ideias \textit{website}}.
\end{tightitemize}

\sectionspace

\runsubsection{Variograma}
\descript{| Programmer}

\location{April 2010 - July 2010 | Lisboa, PT}
\begin{tightitemize}
	\item Development of \textit{web} bussiness solutions;
	\item Development of the company's \textit{website}, and \textit{websites} for companies such as, \textbf{Grupo José Maria da Fonseca}, \textbf{Banco Alimentar Contra a Fome}, amongst others.
\end{tightitemize}

\sectionspace

\section{Skills}

\runsubsection{Programming}\\
.NET \textbullet{} PHP \textbullet{} Javascript \textbullet{} HTML \textbullet{} CSS \textbullet{} SQL \textbullet{} \LaTeX{}\\
\runsubsection{Administration}\\
VMware Infrastructures \textbullet{} Microsoft Server Enviroments \textbullet{} CISCO Networks\\
\runsubsection{Implementation}
VMware vSphere \textbullet{} Microsoft Active Directory \textbullet{} Microsoft DHCP/DNS \textbullet{} Microsoft Terminal Services \textbullet{} Microsoft IIS \textbullet{} Microsoft Printing/File Sharing \textbullet{} Network Infrastructures

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}